---
title: "Credit Card Customer Segmentation"
subtitle: BA820 - Fall 2019
author: "team 7"
date: "12/09/2019"
output: html_document
---

**Team 7 Members:** Kunpeng Huang, Yoki Liu, Lyufan Pan, Yunlei Zhou, Jiayuan Zou, Sherry Zuo
```{r}
## load the packages
library(readr)
library(ggplot2)
library(dplyr)
library(purrr)
library(cluster)
library(factoextra)
library(tidyverse)
library(skimr)
library(corrplot)
library(plotly)
library(Rtsne)
library(tidytext)
library(wordcloud)
library(quanteda)
library(tm)
library(ggpubr)
#install.packages("GGally")
library(GGally)
library(plyr)
library(animation)
#install.packages("viridis")
#install.packages('viridisLite')
library(viridis)
detach(package:plyr)
#install.packages('fmsb')
library(fmsb)
library(RColorBrewer)
library(scales)
library(yarrr)
#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
library(ggradar)
library(plyr)
```

#######Part 1 data #######
```{r}
## load the dataset
data<-read_csv("CC GENERAL.csv")
```

```{r}
colnames(data)<-tolower(colnames(data))
colnames(data)
```

```{r}
##Data Cleaning
cc<-data%>%select(-cust_id)
colmean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
cc <- replace(cc, TRUE, lapply(cc, colmean))
glimpse(cc)
skim(cc)
##There are 17 numeric variables and 8950 observations. Replace NAs with colmeans. 
```
```{r}
summary(lm(credit_limit~. , cc))
```

```{r fig.width=12, fig.height=12}
cc_c<-cor(cc)
corrplot(cc_c,
         type="upper",
         diag=F,
         method="color",
         order="hclust")
```
Based on the correlation plot colors, we think there are more than 4 clusters in our dataset.
```{r}
##Explore data
ggplot(cc,aes(x=purchases_frequency)) +
  geom_histogram()+
  theme(panel.background = element_rect(fill="white"))
```
Based on this histigram, this graph shows us that the purchasing polarization. x-axis indicates that how frequently the purchases are being made, 1 = very frequently, and 0 = not very frequently. Most of transcations is concetred on the either not very frequently or very frequently group.
```{r}
ggplot(cc, aes(x = balance_frequency, y = balance, color = factor(tenure)))+
  geom_point(alpha = 0.2)+
  theme(panel.background = element_rect(fill="white"))
```
```{r}
##cash_advance_frequency with cash_advance_trx
##purchases with purchases_installments_frequency
##purchases_frequency with purchases_installments_frequency
ggplot(cc, aes(x = purchases_installments_frequency, y = purchases, color = purchases_frequency))+
  geom_point()+
  theme(panel.background = element_rect(fill="white"))
```
 
```{r}
##balance
par(mfrow = c(2,1))
hist(x=cc$balance)
boxplot(cc$balance, horizontal = T)->q1
##balance freq: both withdraw and saving
par(mfrow = c(2,1))
hist(x=cc$balance_frequency)
boxplot(cc$balance_frequency, horizontal = T)->q2
##purchases
par(mfrow = c(2,1))
hist(x=cc$purchases)
boxplot(cc$purchases, horizontal = T)->q3
##purchase freq
par(mfrow = c(2,1))
hist(x=cc$purchases_frequency)
boxplot(cc$purchases_frequency, horizontal = T)->q4
##oneoff purchase: maximum purchase amount
par(mfrow = c(2,1))
hist(x=cc$oneoff_purchases)
boxplot(cc$oneoff_purchases, horizontal = T)->q5
##oneoff purchase frequency: maximum purchase refresh freq
par(mfrow = c(2,1))
hist(x=cc$oneoff_purchases_frequency)
boxplot(cc$oneoff_purchases_frequency, horizontal = T)->q6
##oneoff purchase: maximum installment amount
par(mfrow = c(2,1))
hist(x=cc$installments_purchases)
boxplot(cc$installments_purchases, horizontal = T)->q7
```

#######Part 2 PCA+Kmeans #######
```{r}
## Hclust
cc_z = scale(cc)
#Manhattan distance: 
cc_dm = dist(cc_z, method="manhattan")
#Complete linkage: 
clust = hclust(cc_dm)
table(cutree(clust, k=7))
sapply(7:13, function(x) table(cutree(clust, k=x)))
```

```{r}
##Fit the PCA model
cc_pca=prcomp(cc, center=TRUE, scale=TRUE)
```
```{r fig.width=6, fig.height=6}
fviz_pca_var(cc_pca, col.var="contrib", 
             gradient.cols=c("#00AFBB","#E7B800","#FC4E07"),
             repel=TRUE)
##we pick purchase, purchases_trx, balance, cash_advance, cash_advance_frequency, cash advance_trx, purchase_frequency, oneoff_purchases, installments_purchases, purchases_installments_frequency, credit_limit
```

```{r}
fviz_nbclust(scale(cc), kmeans, method = "silhouette", k.max=15)
## choose cluster is 13(7 is also high)
fviz_nbclust(scale(cc), kmeans, method = "wss", k.max=15)
## choose cluster is 2, 4, 7, 9
```


```{r}
##Choose Dimensions
get_eigenvalue(cc_pca)
```
Based on the eigenvalue, we want to choose eigenvalue>1, but we want cumulative variance too small, so we choose Dimension with 8 which has a 85% of cumulative variance. 

```{r}
set.seed(820)
k1=kmeans(scale(cc), 7, 25, 25)
fviz_cluster(k1, scale(cc))
k2=kmeans(scale(cc), 9, 25, 25)
fviz_cluster(k2, scale(cc))
k3=kmeans(scale(cc), 13, 25, 25)
fviz_cluster(k3, scale(cc))
```

```{r}
tt1=data.frame(table(k1$cluster))
tt2=data.frame(table(k2$cluster))
tt3=data.frame(table(k3$cluster))
listP<-list()
listP[[1]]=data.frame(t(tt1))[2,]
listP[[2]]=data.frame(t(tt2))[2,]
listP[[3]]=data.frame(t(tt3))[2,]
do.call(rbind.fill,listP)
```

In the original model, we think k=9 is the best since each cluster has similar size. 


#PCA
```{r}
## apply the features -- could use new data, or the original as I do below
c_pcs=predict(cc_pca, newdata=cc)
class(c_pcs)
c_pcs=as.data.frame(c_pcs)
head(c_pcs)
```
```{r}
c_pc=c_pcs[, 1:8]
head(c_pc)
```

```{r}
fviz_nbclust(scale(c_pc), kmeans, method = "silhouette", k.max=15)
## choose cluster is 2
```
```{r}
fviz_nbclust(scale(c_pc), kmeans, method = "wss", k.max=15)
## choose cluster is 2, 5, 7, 9
```

```{r}
set.seed(820)
k4=kmeans(scale(c_pc), 2, 25, 25)
fviz_cluster(k4, scale(c_pc))
k5=kmeans(scale(c_pc), 5, 25, 25)
fviz_cluster(k5, scale(c_pc))
k6=kmeans(scale(c_pc), 7, 25, 25)
fviz_cluster(k6, scale(c_pc))
k7=kmeans(scale(c_pc), 9, 25, 25)
fviz_cluster(k7, scale(c_pc))
```

```{r}
tt4=data.frame(table(k4$cluster))
tt5=data.frame(table(k5$cluster))
tt6=data.frame(table(k6$cluster))
tt7=data.frame(table(k7$cluster))
listP<-list()
listP[[1]]=data.frame(t(tt4))[2,]
listP[[2]]=data.frame(t(tt5))[2,]
listP[[3]]=data.frame(t(tt6))[2,]
listP[[4]]=data.frame(t(tt7))[2,]
do.call(rbind.fill,listP)
```

Since we don't want the size of the cluster too small or larger and try to average the size of clusters, so we think the best k is 5 for the PCA model.  

```{r}
##Results business related
##Add clustering back to the original dataset
c_pc$cluster<-k5$cluster
```
```{r}
plot_ly(x=c_pc[,1], y=c_pc[,2], z=c_pc[,3], type="scatter3d", mode="markers",color =factor(c_pc$cluster))
```
```{r}
cc$cluster<-k5$cluster
head(cc)
```


```{r}
##Try different variables plotting with different cluster
#1
ggplot(cc, aes(x=cluster, y=purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,4000)->p1
#2
ggplot(cc, aes(x=cluster, y=purchases_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,1)->p2
#3
ggplot(cc, aes(x=cluster, y=credit_limit, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,10000)->p3
#4
ggplot(cc, aes(x=cluster, y=balance, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,7000)->p4
#5
ggplot(cc, aes(x=cluster, y=balance_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0.7,1)->p5
#6
ggplot(cc, aes(x=cluster, y=oneoff_purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,5000)->p6
ggarrange(p1,p2,p3,p4,p5,p6,ncol = 2, nrow = 3)
```

```{r}
#7
ggplot(cc, aes(x=cluster, y=purchases_installments_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))->p7
#8
ggplot(cc, aes(x=cluster, y=purchases_trx, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(1,100)->p8
#9
ggplot(cc, aes(x=cluster, y=cash_advance, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,2000)->p9
#10
ggplot(cc, aes(x=cluster, y=cash_advance_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,0.5)->p10
#11
ggplot(cc, aes(x=cluster, y=cash_advance_trx, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,40)->p11
#12
ggplot(cc, aes(x=cluster, y=installments_purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0, 5000)->p12
ggarrange(p7,p8,p9,p10,p11,p12,ncol = 2, nrow = 3)
```
```{r}
ggplot(cc, aes(x=cluster, y=prc_full_payment, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))->p13
p13
```
```{r}
cc %>% select(purchases,purchases_frequency,credit_limit,balance,balance_frequency,oneoff_purchases,purchases_installments_frequency,purchases_trx,cash_advance,cash_advance_frequency,cash_advance_trx,installments_purchases,prc_full_payment,cluster) %>%group_by(cluster) %>% 
  summarise(purchases=mean(purchases),purchases_frequency=mean(purchases_frequency),credit_limit=mean(credit_limit),balance=mean(balance),balance_frequency=mean(balance_frequency),balance_frequency=mean(balance_frequency),oneoff_purchases=mean(oneoff_purchases),pur_install_freq=mean(purchases_installments_frequency),pur_trx=mean(purchases_trx),cash_advance=mean(cash_advance),cash_advance_frequency=mean(cash_advance_frequency),cash_advance_trx=mean(cash_advance_trx),installments_purchases=mean(installments_purchases),prc_full_payment=mean(prc_full_payment)) %>% as.data.frame() ->radar1
rownames(radar1) <-paste("cluster" , letters[1:5] , sep="-")
radar1 %>% select(-cluster)->radar1
```

```{r}
# Set graphic colors
coul <- brewer.pal(5, "Dark2")
colors_border <- coul
colors_in <- alpha(coul,0.3)

radarchart(radar1, axistype=0 , maxmin=F,
    pcol=colors_border, colors_in, plwd=3 , plty=1.5,
    cglcol="grey", cglty=1, axislabcol="black", cglwd=0.8, 
    vlcex=0.8 
    )
legend(x=1.6, y=1.2, legend = paste("cluster" , 1:5), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1, pt.cex=2)
```

```{r}
radar1$cluster<-c(1:5)
p <- ggRadar(radar1, aes(group = cluster), 
     rescale = FALSE, legend.position = "none",
     size = 1, interactive = FALSE, use.label = TRUE) +4
     facet_wrap(~cluster)
```


```{r}
#new try
#13
ggplot(cc, aes(x=cluster, y=prc_full_payment, fill=factor(cluster)))+
  geom_boxplot()+geom_violin(fill='white', alpha=0.5)+
  theme(panel.background = element_rect(fill="white"))
pirateplot(formula = prc_full_payment ~ cluster,
           data = cc,
           theme = 3)
```
Add clustering back to the original dataset, compare variables for clusters based on different boxplots,  and summarize the features of each cluster and define the characteristics of each cluster of card users.  
**Features: **  
Cluster 1: high credit, low purchase, no installment, high cash advance  
Cluster 2: median credit, no cash advance, high purchase, high purchase frequency, high installment and like to run out of credit but then pay full-back  
Cluster 3: low credit, try every feature of the card  
Cluster 4: low credit, low activities in every feature  
Cluster 5: median credit, high purchase, high purchase frequency, high installments,  but low full pay back  
**Characteristics:**    
Cluster 1: (921) long-time users for daily purchases and like cash in advance    
Cluster 2: (1224) users live from paycheck to paycheck    
Cluster 3: (727) new card users    
Cluster 4: (3878) inactive cardholders    
Cluster 5: (2200) installment users with high spending behavior    


#######Part 3  t-SNE+kmeans #######  
```{r}
##tSNE
cc2<-cc%>%select(-cluster)
cc_tsne=Rtsne(cc2,
               verbose=TRUE,
               max_iter=500,
               check_duplicates=FALSE)

## remember that this is for plotting, so we can get the 2d space from Y
class(cc_tsne)
names(cc_tsne)


## lets create the plot
tsne_proj=cc_tsne$Y
class(tsne_proj)
dim(tsne_proj)
head(tsne_proj)
nrow(cc) ==nrow(tsne_proj)
tsne_df=as.data.frame(tsne_proj)
plot(tsne_df$V1, tsne_df$V2, type="p", pch=19)

## just a big hairball, but lets clean it up and map onto it
cc_final=cbind(cc, tsne_df)
```
```{r}
fviz_nbclust(scale(tsne_proj), kmeans, method = "silhouette", k.max=15)
## choose cluster is 6
fviz_nbclust(scale(tsne_proj), kmeans, method = "wss", k.max=15)
## choose cluster is 3, 4, 7, 8
```
```{r}
z2<-scale(as.data.frame(tsne_proj))
k8=kmeans(z2, 3, 25, 25)
fviz_cluster(k8, z2)->f8
k9=kmeans(z2, 4, 25, 25)
fviz_cluster(k9, z2)->f9
k10=kmeans(z2, 6, 25, 25)
fviz_cluster(k10, z2)->f10
k11=kmeans(z2, 7, 25, 25)
fviz_cluster(k11, z2)->f11
k12=kmeans(z2, 8, 25, 25)
fviz_cluster(k12, z2)->f12
k13=kmeans(z2, 5, 25, 25)
fviz_cluster(k13, z2)->f13
f8
f9
f10
f11
f12
f13
```
```{r}
t3=data.frame(table(k8$cluster))
t4=data.frame(table(k9$cluster))
t6=data.frame(table(k10$cluster))
t7=data.frame(table(k11$cluster))
t8=data.frame(table(k12$cluster))
t5=data.frame(table(k13$cluster))
listQ<-list()
listQ[[1]]=data.frame(t(t3))[2,]
listQ[[2]]=data.frame(t(t4))[2,]
listQ[[3]]=data.frame(t(t5))[2,]
listQ[[4]]=data.frame(t(t6))[2,]
listQ[[5]]=data.frame(t(t7))[2,]
listQ[[6]]=data.frame(t(t8))[2,]
do.call(rbind.fill,listQ)
```

chose k=5
```{r}
cc2$cluster<-k13$cluster
```

```{r}
##Try different variables plotting with different cluster
ggplot(cc2, aes(x=cluster, y=purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,4000)->g1
ggplot(cc2, aes(x=cluster, y=purchases_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,1)->g2
ggplot(cc2, aes(x=cluster, y=credit_limit, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,10000)->g3
ggplot(cc2, aes(x=cluster, y=balance, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,6000)->g4
ggplot(cc2, aes(x=cluster, y=balance_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0.5,1)->g5
ggplot(cc2, aes(x=cluster, y=oneoff_purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,2000)->g6
ggarrange(g1,g2,g3,g4,g5,g6,ncol = 2, nrow = 3)
```
```{r}
ggplot(cc2, aes(x=cluster, y=purchases_installments_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))->g7
ggplot(cc2, aes(x=cluster, y=purchases_trx, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(1,100)->g8
ggplot(cc2, aes(x=cluster, y=cash_advance, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,2000)->g9
ggplot(cc2, aes(x=cluster, y=cash_advance_frequency, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,0.5)->g10
ggplot(cc2, aes(x=cluster, y=cash_advance_trx, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0,30)->g11
ggplot(cc2, aes(x=cluster, y=installments_purchases, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))+
  ylim(0, 4000)->g12
ggarrange(g7,g8,g9,g10,g11,g12,ncol = 2, nrow = 3)
```
```{r}
ggplot(cc2, aes(x=cluster, y=prc_full_payment, fill=factor(cluster)))+
  geom_boxplot()+
  theme(panel.background = element_rect(fill="white"))->g13
g13
```

```{r}
cc2 %>% select(purchases,purchases_frequency,credit_limit,balance,balance_frequency,oneoff_purchases,purchases_installments_frequency,purchases_trx,cash_advance,cash_advance_frequency,cash_advance_trx,installments_purchases,prc_full_payment,cluster) %>%group_by(cluster) %>% 
  summarise(purchases=mean(purchases),purchases_frequency=mean(purchases_frequency),credit_limit=mean(credit_limit),balance=mean(balance),balance_frequency=mean(balance_frequency),balance_frequency=mean(balance_frequency),oneoff_purchases=mean(oneoff_purchases),pur_install_freq=mean(purchases_installments_frequency),pur_trx=mean(purchases_trx),cash_advance=mean(cash_advance),cash_advance_frequency=mean(cash_advance_frequency),cash_advance_trx=mean(cash_advance_trx),installments_purchases=mean(installments_purchases),prc_full_payment=mean(prc_full_payment)) %>% as.data.frame() ->radar2
rownames(radar2) <-paste("cluster" , letters[1:5] , sep="-")
radar2 %>% select(-cluster)->radar2
coul <- brewer.pal(5, "Dark2")
colors_border <- coul
colors_in <- alpha(coul,0.3)

radarchart(radar2, axistype=0 , maxmin=F,
    pcol=colors_border, pfcol=colors_in, plwd=3 , plty=1.5,
    cglcol="grey", cglty=1, axislabcol="black", cglwd=0.8, 
    vlcex=0.8 
    )
legend(x=1.6, y=1.2, legend = paste("cluster" , 1:5), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1, pt.cex=2)
```

Based on the result of t-SNE model, we try k with 4 to 8 and finally get the clustering model with each of them.  

Unfortunately, after getting the features of each cluster, we get the idea that features not clear in the tSNE method, especially when we compare the features model with PCA.   

Here is the example of k=5. In the cluster plot, it is hard to find a clear division of groups, kmean just divides the entire two-dimensional space evenly. Plus, in the radar plot of each cluster, the unclear differences between groups make it difficult to describe customer characteristics in the real world.  

```{r}
##try text mining
text<-list(
  colnum = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15),
  mains = c(
"Credit Card User Segmentation",
"Business Problem
The purpose of this project is to explore the customer segmentation based on their purchase behavior with credit card and to help the credit card company to design different marketing strategy for various target customer based on characteristic explored of each cluster",
"Dataset	
Credit Card Dataset for Clustering
The sample Dataset summarizes the usage behavior of 8950 active credit cardholder during the last 6 months. The file is at a customer level with 18 variables.",
"Data Cleaning
In the dataset, there are 313 missing values in variable minimum_payment, and we used the mean of the minimum payment to replace the missing values. Since customer id is not used in the analysis, we removed it from the dataset. After data cleaning, we have 17 numeric variables and 8950 observation",
"Data Exploration
Balance: The left balance of majority user are below $5000 with an average of $1564.47 
Balance Frequency: The majority of the cardholder are active and have a balance frequency around 1
Purchase frequency:  The graph shows us that the purchase polarization. Most credit card record is concentrated on either not very frequently or very frequently group
One-off purchase: The mean of one-off purchase is $592.4, and most credit cardholder uses this credit card in the routine purchase
One-off purchase frequency: since this card is widely used in daily life, the one-off purchase frequency is pretty low (mean = 0.083). Which stands for those customer who were not tent to purchase expensive items
Installment_purchase: Those groups of users were not relying on using this card to purchase expensive items based on the installment payment method ( mean = $411.1) 
Purchase_Installment_Frequency: 43.7% of cardholder were very inactive (frequency = 0 ) on using installment payment method, and 14.9% of cardholder were heavily relied (frequency = 0) on using the installment payment method 
Cash_Advanc_TRX: Most users were not active in withdrawing cash. However, we detected that a limited customer whose number of transaction made with cash is pretty big, and we need to care more about their purchase behavior. Since the primary goal of using credit is not withdraw cash  
Cash_Advance_Frequency: Most user were not frequently withdrawn cash 
Credit_Limit: Most users credit limit’s range is below $5,000
Prc_Full_Payment: the mean percent of full payment paid by the user is pretty low ( mean = 0.15) we need to launch new strategy to encourage users to pay back the money as much as they can",
"Analysis Methodology
Baseline clustering Model 
Silhouette score: choose cluster is 13 (7 and 9 is also very high, similar for every size of k)
WSS-choose cluster is 2, 4, 7, 9: sum of square error is too large
Compare those cluster plots, we think k=9 is the best since each cluster has a similar size in the baseline clustering. ",
"Dimension Reduction Model (t-SNE model+Kmeans)
 
 
Based on the result of t-SNE model,  we try k with 4 to 8 and finally get the clustering model with each of them.
 
Unfortunately, after getting the feature of each cluster, we get the idea that feature not clear in the tSNE method, especially when we compare the feature model with PCA later. 
Here is the example of k=5. In the cluster plot, it is hard to find clear division of group, kmean just divides the entire two-dimension space evenly. Plus, in the radar plot of each cluster, the unclear difference between groups make it difficult to describe customer characteristic in the real world.",
"Correlation Plot 
Based on the correlation plot colors, we think there are more than 4 group in our dataset.",
"Dimension Reduction Model (PCA model+Kmeans)
Compare Eigenvalue and Cumulative Variance
eigenvalue
variance.percent
cumulative.variance.percent
Dimension.5
1.0646746466
6.262797e+00
70.12678
Dimension.8
0.7237725420
4.257486e+00
85.02171
Based on the eigenvalue, we want to choose eigenvalue>1, so we could choose Dimension with 5; however, since we don’t want cumulative variance too small, so we choose Dimension with 8 which has a higher cumulative variance (around 85%).",
"Clustering for PCA model
Silhouette score-choose cluster is 2
WSS-choose cluster is 2, 5, 7, 9
Since we don't want the size of the cluster too small or larger and try to average the size of cluster, so we think the best k is 5 for the PCA model.",
"Our best model overall:Thus, our best model is Dimension 8 and cluster 5. ",
"Performance Evaluation:
Add clustering back to the original dataset, compare variables for cluster based on different boxplots,  and summarize the feature of each cluster and define the characteristic of each cluster of card user.",
"Feature: 
Cluster 1: high credit, low purchase, no installment, high cash advance
Cluster 2: median credit, no cash advance, high purchase, high purchase frequency, high installment and like to run out of credit but then pay full-back
Cluster 3: low credit, try every feature of the card
Cluster 4: low credit, low activities in every feature
Cluster 5: median credit, high purchase, high purchase frequency, high installment,  but low full pay back",
"Characteristic:
Cluster 1: (921) long-time users for daily purchase and like cash in advance
Cluster 2: (1224) users live from paycheck to paycheck
Cluster 3: (727) new card users
Cluster 4: (3878) inactive cardholder
Cluster 5: (2200) installment users with high spending behavior",
"Results business related  
Marketing Strategy Recommendation  
Based on those 5 feature, we design different marketing strategy for various target customer.  
**Cluster1: **long-time user for daily purchase and like cash in advance  
Generalize cashback focused credit card. Having policy like unlimited 1% cash back on every purchase or on up to a certain amount in combined purchase in bonus category (like gas stations, grocery stores, etc.) each quarter. Customer in cluster1 that use credit card for small purchase and daily purchase are usually very economical and will be attracted by adding on benefit.  
**Cluster2: **user live from paycheck to paycheck  
Generalize bonus point focused credit card with a certain amount of annual fee. Having policy like earning a certain amount of bonus points after the customer spends 3,000 dollars on purchase in the first three months from account opening, and that allows them to redeem the points for shopping, travel, or etc. Furthermore, if the customer spend more on traveling, we can also have policies like 300 dollars annual travel credit as reimbursement or double points on travel expenses. Customer in cluster 2 with high spending behavior care more about their living quality and are willing to spend money on enjoyment.  
**Cluster3: **new card user   
Generalize special incentives for new card user. Sending out introduction mails to give them a brief summary of how credit card work and target them with titles like “pre-approved”, “benefit card” and lead them to keep using the card. Offer 3% cash back on selected category and let the customer choose which category they would like to activate. The majority of the new card user are students and targeting their own spending interest will be a good way to make them forming the habits of using credit card.  
**Cluster4: **inactive cardholder  
Generalize a comprehensive credit card to target inactive cardholder. People don’t use credit card that often might prefer to use debit card to prevent from spending too much money or have lots of credit card to choose from. An all-sided credit card may quality their needs and attract them to use our credit card more often than the others. For example like no annual fee, free or low apr, and unlimited 2-3% cash back on all purchase. Customer in cluster 4 is difficult to perceive and offering all-sided strategy will be an appropriate way to target them.  
**Cluster5: **installment user with high spending behavior  
Generalize benefit like priority airport lounges, room upgrades, and special gifts for purchase focused credit card but with a certain amount of APR required. We may target installment user with free APR for the first six months, and offering free balance transfer function to satisfy their needs. Customer in cluster 5 usually spend a lot but prefer to do installment, thus premium benefit with limited time of free APR will be exactly what they need when applying for credit card."
)
)
```

```{r}
text$mains=str_to_lower(text$mains)
text=as.data.frame(text)
text$mains=as.character(text$mains)
text$mains = gsub("_", " ", text$mains)
text$mains = removeNumbers(text$mains)
credit_tokens = text %>% 
  unnest_tokens(token, mains, strip_punct=T) %>% 
  anti_join(get_stopwords(), get_stopwords(source="snowball"), get_stopwords(source="stopwords-iso"), get_stopwords(source="smart"), by=c("token"="word"))
##address these common words that are not adding value
credit_tokens %>% 
  count(token, sort=T) %>% 
  head(n=25)%>%
  ggplot(aes(x=token, y=n))+
  geom_bar(stat="identity", fill="#E7B800")+
  theme(panel.background = element_rect(fill="white"))+
  theme(axis.text.x=element_text(angle=30))##get useful top words
tidy_tokens=credit_tokens%>%
  count(token, sort=T)
par(mfrow = c(1,1))
wordcloud(words=tidy_tokens$token,
          freq=tidy_tokens$n,
          min.freq=5,
          max.words=45,
          colors=brewer.pal(8, "Dark2"))
```

Results business related  
Marketing Strategies Recommendation  
Based on those 5 features, we design different market strategies for various target customers.  
**Cluster1: **long-time users for daily purchases and like cash in advance  
Generalize cashback focused credit card. Having policies like unlimited 1% cash back on every purchase or on up to a certain amount in combined purchases in bonus categories (like gas stations, grocery stores, etc.) each quarter. Customers in cluster1 that use credit cards for small purchases and daily purchases are usually very economical and will be attracted by adding on benefits.  
**Cluster2: **users live from paycheck to paycheck  
Generalize bonus point focused credit card with a certain amount of annual fee. Having policies like earning a certain amount of bonus points after the customer spends 3,000 dollars on purchases in the first three months from account opening, and that allows them to redeem the points for shopping, travel, or etc. Furthermore, if the customers spend more on traveling, we can also have policies like 300 dollars annual travel credit as reimbursement or double points on travel expenses. Customers in cluster 2 with high spending behaviors care more about their living quality and are willing to spend money on enjoyment.  
**Cluster3: **new card users   
Generalize special incentives for new card users. Sending out introduction mails to give them a brief summary of how credit cards work and target them with titles like “pre-approved”, “benefit cards” and lead them to keep using the cards. Offer 3% cash back on selected category and let the customers choose which category they would like to activate. The majority of the new card users are students and targeting their own spending interest will be a good way to make them forming the habits of using credit cards.  
**Cluster4: **inactive cardholders  
Generalize a comprehensive credit card to target inactive cardholders. People don’t use credit card that often might prefer to use debit cards to prevent from spending too much money or have lots of credit cards to choose from. An all-sided credit card may quality their needs and attract them to use our credit card more often than the others. For example like no annual fee, free or low apr, and unlimited 2-3% cash back on all purchases. Customers in cluster 4 is difficult to perceive and offering all-sided strategy will be an appropriate way to target them.  
**Cluster5: **installment users with high spending behavior  
Generalize benefits like priority airport lounges, room upgrades, and special gifts for purchases focused credit cards but with a certain amount of APR required. We may target installment users with free APR for the first six months, and offering free balance transfer function to satisfy their needs. Customers in cluster 5 usually spend a lot but prefer to do installments, thus premium benefits with limited time of free APR will be exactly what they need when applying for credit cards.  



